\documentclass{ximera}

\title{Deploying with Xake}

\begin{document}
\begin{abstract}
Using Xake to deploy.
\end{abstract}
\maketitle

The program \verb|xake| is the Ximera ``make'' program.

\section{One-time setup}

Here is a list of commands that need to be run for the setup of a course. 

\begin{enumerate}
\item If you have a GPG key, do:
\begin{verbatim}
gpg --list-keys
\end{verbatim}
\item If you don’t already have a GPG key, then do
\begin{verbatim}
gpg --gen-key
\end{verbatim}
answer the questions, but \textbf{leave the passphrase blank} and copy
the long hex string as YOUR-GPG-KEY-ID (ABCD3562DBF9929292 or
whatever).

If you are using MacOS, you might not be able to leave the passphrase
blank. In this case go to \link{https://gpgtools.org/} and install the
GPG Suite.  This will provide a GUI that will produce a GPG key with
spaces. Delete these spaces and this new key (without spaces) is your
key. You should quite your terminal and open a new one.

\begin{verbatim}
gpg --keyserver hkps://ximera.osu.edu/ --send-key YOUR-GPG-KEY-ID
\end{verbatim}
Now do
\item Now do: 
\begin{verbatim}
xake -k YOUR-GPG-KEY-ID name yourxakename
\end{verbatim}

\item You may get vague error messages here if you have not successfully set up your git name and email; you can do this with:
\begin{verbatim}
git config --global user.name "YOUR-NAME"
git config --global user.email "YOUR-EMAIL"
\end{verbatim}
\end{enumerate}


\section{Work flow}

The commands above are simply for setup. On a regular basis, the work flow is much simpler.

You must work in the top level of your git directory.
\begin{verbatim}
git pull
git add -u
git commit
git push
xake bake
xake frost
xake serve
\end{verbatim}




  

\end{document}
